Manuscript_1

### 2025-01-30 Manuscript_1.Rmd
Code for figures update

# Check singularity version
singularity version   # 3.9.0

@@

@@

# Issue between dplyr, BiocFilrCache and biomaRt - > downgrade dbplyr
install.packages("devtools")
devtools::install_version("dbplyr", version = "2.3.4")
```

@@

```{r load_lib, eval = FALSE, echo = TRUE}
# Load
library("tidyverse")
library("rstatix")
library("ggpubr")
library("plotgardener")
#library("BSgenome.Hsapiens.UCSC.hg38")
#library("TxDb.Hsapiens.UCSC.hg38.knownGene")
library("TxDb.Hsapiens.UCSC.hg38.refGene")
library("org.Hs.eg.db")
library("extrafont")
library("showtext")
library("JASPAR2020")
library("TFBSTools")
library("ggseqlogo")
library("biomaRt")
library("LDlinkR")
library("AllelicImbalance")
library("png")
library("AnnotationDbi")
library("scales")
library("flowCore")
library("ggcyto")

# Check
packageVersion("tidyverse") #2.0.0
packageVersion("rstatix") #0.7.2
packageVersion("ggpubr")  #0.6.0
packageVersion("plotgardener")  #1.4.2
#packageVersion("BSgenome.Hsapiens.UCSC.hg38") #1.4.5
#packageVersion("TxDb.Hsapiens.UCSC.hg38.knownGene") #3.16.0
packageVersion("TxDb.Hsapiens.UCSC.hg38.refGene") #3.15.0
packageVersion("org.Hs.eg.db")  #3.16.0
packageVersion("extrafont") #0.19
packageVersion("showtext")  #0.9.6
packageVersion("JASPAR2020")  #0.99.10
packageVersion("TFBSTools") #1.36.0
packageVersion("ggseqlogo") #0.1
packageVersion("biomaRt") #2.54.1
packageVersion("LDlinkR") #1.3.0
packageVersion("AllelicImbalance")  #1.36.0
packageVersion("png") #0.1.8
packageVersion("AnnotationDbi") #1.60.2
packageVersion("dbplyr")  #2.3.4

@@

# FIGURES
### FIGURE 1
```{r fig1, eval = FALSE, echo = TRUE}
########## FIGURE 1 ##########
##############################
# Save as a PDF
pdf("/home/vagrant/Manuscript_1/FIGURE1/FIGURE1.pdf",
    width = 8.3, 
    height = 11.7)

#### PANEL A - 
# text Figure 1
plotText(label = "Figure 1", 
         fontsize = 14,
         x = 0.25, 
         y = 0.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")
# text A
plotText(label = "A", 
         fontsize = 12,
         x = 0.25, 
         y = 0.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# text B
plotText(label = "B", 
         fontsize = 12,
         x = 0.25, 
         y = 1.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# text C
plotText(label = "C", 
         fontsize = 12,
         x = 0.25, 
         y = 4.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# text D
plotText(label = "D", 
         fontsize = 12,
         x = 0.25, 
         y = 8.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

###################
#### Figure 1A ####
###################
Fig1A = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1A.png")

# Plot Figure 1A
plotRaster(image = Fig1A,
           x = 0.375,
           y = 0.625,
           width = 7.55,
           height = 1.0,
           just = c("left", 
                    "top"),
           interpolate = FALSE)

###################
#### Figure 1B ####
###################
# Load data obtained from Jochen
RNAseq_odd = read_delim("/home/vagrant/Manuscript_1/FIGURE1/REFORMAT_tpm_gene_sets.gsa.txt",
                        delim = "\t",
                        col_names = TRUE)

#RNAseq_odd = read_delim("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/REFORMAT_tpm_gene_sets.gsa.txt",
#                        delim = "\t",
#                        col_names = TRUE)

@@

# Plot
fig1B = ggplot(RNAseq_odd,
       aes(x = odd_R,
           y = VARIABLE)) +
  geom_point(shape = 16, size = 3) +
  geom_errorbarh(aes(xmin = odd_R - SE, 
                     xmax = odd_R + SE), 
                 height = 0.25) +
  geom_vline(xintercept = 1.0, linetype = "dashed", color = "grey") +
  theme_classic() +
  theme(axis.title = element_text(face = "bold"),
        axis.text = element_text(face = "bold")) +
  scale_y_discrete(labels = c("smNPC" = "smNPC", 
                              "D15negsort" = "non-mDAN D15", 
                              "D15possort" = "mDAN D15", 
                              "D30postsort" = "mDAN D30", 
                              "D50negsort" = "non-mDAN D50",
                              "D50possort" = "mDAN D50",
                              "astrocytes" = "Astrocytes")) +
  geom_text(label = round(RNAseq_odd$P, 
                          digits = 3),
            nudge_y = 0.40) +
  xlab("Odds ratio (95% Confidence Interval)") +
  ylab("")

# Place
plotGG(plot = fig1B, 
       x = 0.375, 
       y = 1.75, 
       width = 3.0, 
       height = 2.5,
       just = c("left", "top"), 
       default.units = "inches")

###################
#### Figure 1C ####
###################
Fig1C_pip = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1C_pipeline.png")

Fig1C_tab1.1 = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1C_SNPs_tab1.png/Fig1C_SNPs_tab1.png-1.png")
Fig1C_tab1.2 = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1C_SNPs_tab1.png/Fig1C_SNPs_tab1.png-2.png")

# Plot Figure 1C
plotRaster(image = Fig1C_pip,
           x = 0.375,
           y = 5.25,
           width = 3.0,
           height = 2.5,
           just = c("left", 
                    "top"),
           interpolate = FALSE)

plotRaster(image = Fig1C_tab1.1,
           x = 3.375,
           y = 5.25,
           width = 2.3,
           height = 2.5,
           just = c("left", 
                    "top"),
           interpolate = FALSE)

plotRaster(image = Fig1C_tab1.2,
           x = 5.8,
           y = 5.25,
           width = 2.3,
           height = 2.5,
           just = c("left", 
                    "top"),
           interpolate = FALSE)

#diag_edge_data = tibble(from = c("~17x10^6\nPD GWAS SNPs",
#                                 "~3400 significant\nPD GWAS SNPs",
#                                 "28 significant\nPD rSNPs"),
#                        to = c("~3400 significant\nPD GWAS SNPs",
#                               "28 significant\nPD rSNPs",
#                               "3 significant\nPD rSNPs"))
#
#diag_node_data = tibble(name = c("~17x10^6\nPD GWAS SNPs",
#                                 "~3400 significant\nPD GWAS SNPs",
#                                 "28 significant\nPD rSNPs",
#                                "3 significant\nPD rSNPs"),
#                        label = name)

# Diagramme
# fig1C = ggflowchart(diag_edge_data,
#                    diag_node_data,
#                    text_size = 3.0,
#                    arrow_size = 0.2)

# Place the diagramme
#plotGG(plot = fig1C, 
#       x = 0.5, 
#       y = 4.5, 
#      width = 1.5, 
#       height = 3.0,
#       just = c("left", "top"), 
#      default.units = "inches")

>>>>

##
#rsync -avzPhu iris-cluster:/home/users/dgerard/Singularity_containers/Manuscript_1_singularity.sif ~/Downloads/

#scp -r -P 2222 -i /Users/deborah.gerard/singularity-vm/.vagrant/machines/default/virtualbox/private_key \
#~/Downloads/Manuscript_1_singularity.sif vagrant@127.0.0.1:/home/vagrant/Manuscript_1_singularity/

##
# Check singularity version
singularity version   # 3.9.0

@@

# TEST
sudo singularity build --sandbox Manuscript_1_singularity_tmp Manuscript_1_singularity.sif

@@

# Issue between dplyr, BiocFilrCache and biomaRt - > downgrade dbplyr
install.packages("devtools")
devtools::install_version("dbplyr", version = "2.3.4")

# ggmanh
BiocManager::install("ggmanh")
```

@@

```{r load_lib, eval = FALSE, echo = TRUE}
# Load
library("tidyverse")
library("rstatix")
library("ggpubr")
library("plotgardener")
#library("BSgenome.Hsapiens.UCSC.hg38")
library("TxDb.Hsapiens.UCSC.hg38.knownGene")
library("TxDb.Hsapiens.UCSC.hg38.refGene")
library("org.Hs.eg.db")
library("extrafont")
library("showtext")
library("JASPAR2020")
library("TFBSTools")
library("ggseqlogo")
library("biomaRt")
library("LDlinkR")
library("AllelicImbalance")
library("png")
library("AnnotationDbi")
library("scales")
library("flowCore")
library("ggcyto")
library("ggmanh")
library("rtracklayer")
library("plyranges")
library("RColorBrewer")

# Check
packageVersion("tidyverse") #2.0.0
packageVersion("rstatix") #0.7.2
packageVersion("ggpubr")  #0.6.0
packageVersion("plotgardener")  #1.4.2
#packageVersion("BSgenome.Hsapiens.UCSC.hg38") #1.4.5
#packageVersion("TxDb.Hsapiens.UCSC.hg38.knownGene") #3.16.0
packageVersion("TxDb.Hsapiens.UCSC.hg38.refGene") #3.15.0
packageVersion("org.Hs.eg.db")  #3.16.0
packageVersion("extrafont") #0.19
packageVersion("showtext")  #0.9.7
packageVersion("JASPAR2020")  #0.99.10
packageVersion("TFBSTools") #1.36.0
packageVersion("ggseqlogo") #0.2
packageVersion("biomaRt") #2.54.1
packageVersion("LDlinkR") #1.4.0
packageVersion("AllelicImbalance")  #1.36.0
packageVersion("png") #0.1.8
packageVersion("AnnotationDbi") #1.60.2
#packageVersion("dbplyr")  #2.5.0
packageVersion("scales")  #1.3.0
packageVersion("flowCore")  #2.10.0
packageVersion("ggcyto")  #1.26.4
packageVersion("ggmanh")  #1.2.0
packageVersion("rtracklayer") #1.58.0
packageVersion("plyranges") #1.18.0
packageVersion("RColorBrewer")  #1.1.3

@@

# FIGURES
Generating the manhattan plot for the PD GWAS is memory demanding. Go to the HPC
```{bash, eval = FALSE, echo = TRUE}
#ssh iris-cluster
#salloc --nodes=1 -p interactive --qos debug -C batch -t 02:00:00 --mem 24G

# Load the Singularity module
#module load tools/Singularity/3.8.1
#singularity shell --bind /scratch/users/dgerard:/scratch/users/dgerard $HOME/Singularity_containers/Manuscript_1_singularity.sif
```

### FIGURE 1
```{r fig1, eval = FALSE, echo = TRUE}
########## FIGURE 1 ##########
##############################
# Save as TIFF, 300 ppi
tiff("/home/vagrant/Manuscript_1/FIGURE1/FIGURE1.tiff",
     width = 8.27,
     height = 9.5,
     units = "in",
     res = 300,
     compression = "lzw")

# Create a A4 blank page
pageCreate(width = 8.27, 
           height = 9.5, 
           default.units = "inches",
           showGuides = TRUE)

#### PANEL A - 
# text Figure 1
plotText(label = "Figure 1", 
         fontsize = 14,
         fontfamily = "Helvetica",
         x = 0.25, 
         y = 0.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# text A
plotText(label = "A", 
         fontsize = 12,
         fontfamily = "Helvetica",
         x = 0.25, 
         y = 0.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

##########################################
#### Figure 1A Data generation scheme ####
##########################################
# Figure 1A generated in Biorender
fig1A = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1A_Biorender_vertical.png")

plotRaster(image = fig1A,
           x = 0.5, 
           y = 2.5, 
           default.units = "inches",
           width = 2.5, 
           height = 3.75, 
           just = "left",
           interpolate = TRUE)

##########################################
#### Figure 1B Odd ratio #################
##########################################
# text B
plotText(label = "B", 
         fontsize = 12,
         fontfamily = "Helvetica",
         x = 3.0, 
         y = 0.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# Load data obtained from Jochen
RNAseq_odd = read_delim("/home/vagrant/Manuscript_1/FIGURE1/REFORMAT_tpm_gene_sets.gsa.txt",
                        delim = "\t",
                        col_names = TRUE)

@@

# Plot
fig1B = ggplot(RNAseq_odd,
       aes(x = odd_R,
           y = VARIABLE)) +
  geom_point(shape = 16, size = 3) +
  geom_errorbarh(aes(xmin = odd_R - SE, 
                     xmax = odd_R + SE), 
                 height = 0.25) +
  geom_vline(xintercept = 1.0, linetype = "dashed", color = "grey") +
  theme_classic() +
  theme(axis.title = element_text(face = "bold"),
        axis.text = element_text(face = "bold")) +
  scale_y_discrete(labels = c("smNPC" = "smNPC", 
                              "D15negsort" = "non-mDAN D15", 
                              "D15possort" = "mDAN D15", 
                              "D30postsort" = "mDAN D30", 
                              "D50negsort" = "non-mDAN D50",
                              "D50possort" = "mDAN D50",
                              "astrocytes" = "Astrocytes")) +
  geom_text(label = round(RNAseq_odd$P, 
                          digits = 3),
            nudge_y = 0.40) +
  xlab("Odds ratio \n(95% Confidence Interval)") +
  ylab("")

# Place the plot
plotGG(plot = fig1B, 
       x = 3.25, 
       y = 0.5, 
       width = 4.5, 
       height = 4.5,
       just = c("left", "top"), 
       default.units = "inches")

####################################
#### Figure 1C LowC - Chr4 #########
####################################
# text C
plotText(label = "C", 
         fontsize = 12,
         fontfamily = "Helvetica",
         x = 0.25, 
         y = 5.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# Load TH REP1 mCHERRY mDAN neurons D30 (N1) at 50kb resolution
mDAN.D30.50kb = readHic(file = "/home/vagrant/epifunc/LowC_smNPC_THpos_neur/FANC_output_N1_mDAN_D30/hic/juicer_like/N1_mDAN_D30.juicer.50kb.hic",
                     chrom = "chr4",
                     assembly = "hg38",
                     resolution = 50000,
                     res_scale = "BP",
                     norm = "NONE",
                     matrix = "observed")

# Load TH REP1 mCHERRY mDAN neurons D30 (N1) at 25kb resolution
mDAN.D30.25kb = readHic(file = "/home/vagrant/epifunc/LowC_smNPC_THpos_neur/FANC_output_N1_mDAN_D30/hic/juicer_like/N1_mDAN_D30.juicer.25kb.hic",
                     chrom = "chr4",
                     assembly = "hg38",
                     resolution = 25000,
                     res_scale = "BP",
                     norm = "NONE",
                     matrix = "observed")

# Load TH REP1 mCHERRY smNPCs (N1) at 50kb resolution
smNPC.50kb = readHic(file = "/home/vagrant/epifunc/LowC_smNPC_THpos_neur/FANC_output_N1_smNPC/hic/juicer_like/N1_smNPC.juicer.50kb.hic",
                     chrom = "chr4",
                     assembly = "hg38",
                     resolution = 50000,
                     res_scale = "BP",
                     norm = "NONE",
                     matrix = "observed")

# Full chr4 to display
region.p.chr4 = pgParams(chrom = "chr4",
                         assembly = assembly(Genome = "hg38refGene",
                                             TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene",
                                             OrgDb = "org.Hs.eg.db"),
                         just = c("left", "top"),
                         width = 3.5,
                         fontcolor = "black",
                         fill = "black")

# Plot full chr4 - smNPC on top of the diagonale and mDAN D30 at the bottom of the diagonale
LowC_smNPC.top = plotHicSquare(data = smNPC.50kb, 
                               params = region.p.chr4,
                               zrange = c(0, 5), 
                               resolution = "auto",
                               half = "top",
                               x = 0.5,
                               y = 5.5, 
                               height = 3.5)

annoHeatmapLegend(plot = LowC_smNPC.top, 
                  fontsize = 7,
                  x = 0.375, 
                  y = 6.0,
                  width = 0.07, 
                  height = 0.5, 
                  just = c("left", "top"),
                  default.units = "inches")

# smNPC
plotText(label = "smNPC", 
         fontsize = 12,
         fontfamily = "Helvetica",
         x = 0.5625, 
         y = 5.625, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

LowC_mDAND30.bottom = plotHicSquare(data = mDAN.D30.50kb, 
                               params = region.p.chr4,
                               zrange = c(0, 5), 
                               resolution = "auto",
                               half = "bottom",
                               x = 0.5,
                               y = 5.5, 
                               height = 3.5)

annoHeatmapLegend(plot = LowC_mDAND30.bottom, fontsize = 7,
                  x = 4.0625, 
                  y = 6.0,
                  width = 0.07, 
                  height = 0.5,
                  just = c("left", "top"),
                  default.units = "inches")

# mDAN D30
plotText(label = "mDAN D30", 
         fontsize = 12,
         fontfamily = "Helvetica",
         x = 3.0, 
         y = 8.9375, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# Add genome label of chr4
annoGenomeLabel(plot = LowC_mDAND30.bottom, 
                scale = "Mb", 
                axis = "x",
                x = 0.5, 
                y = 9.0625, 
                just = c("left", "top"))

# Annotate SNCA domain that will be zoomed in fid1D
SNCA.TAD = GRanges("chr4",
                   ranges = IRanges(start = 89000000,
                                    end = 91000000))

domainAnno = annoDomains(plot = LowC_mDAND30.bottom, 
                         data = SNCA.TAD,
                         half = "bottom", 
                         linecolor = "red")

###################################
#### Figure 1D SNCA locus #########
###################################
# Zoom on SNCA an add ATACseq dataof the locus
# Define parameters for a small part of chr4 where SNCA is
# Add ATACseq track of smNPC, mDAN D15, mDAN D30, mDAN D50
# text D
plotText(label = "D", 
         fontsize = 12,
         fontfamily = "Helvetica",
         x = 4.125, 
         y = 5.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

bw.path = "/home/vagrant/epifunc/"

# smNPC N1
bw.SNCA.smNPC.1 = readBigwig(file = paste0(bw.path, "BIGWIG/smNPC_I.bw"),
    chrom = "chr4", chromstart = 89000000, chromend = 91000000)

# smNPC N2
bw.SNCA.smNPC.2 = readBigwig(file = paste0(bw.path, "BIGWIG/smNPC_II.bw"),
    chrom = "chr4", chromstart = 89000000, chromend = 91000000)

# smNPC N3
bw.SNCA.smNPC.3 = readBigwig(file = paste0(bw.path, "BIGWIG/smNPC_III.bw"),
    chrom = "chr4", chromstart = 89000000, chromend = 91000000)

# mDAN D15 N1
bw.SNCA.mDAN.D15.1 = readBigwig(file = paste0(bw.path, "BIGWIG/D15_POS_I.bw"),
    chrom = "chr4", chromstart = 89000000, chromend = 91000000)

# mDAN D15 N2
bw.SNCA.mDAN.D15.2 = readBigwig(file = paste0(bw.path, "BIGWIG/D15_POS_II.bw"),
    chrom = "chr4", chromstart = 89000000, chromend = 91000000)

# mDAN D15 N3
bw.SNCA.mDAN.D15.3 = readBigwig(file = paste0(bw.path, "BIGWIG/D15_POS_III.bw"),
    chrom = "chr4", chromstart = 89000000, chromend = 91000000)

# mDAN D30 N1
bw.SNCA.mDAN.D30.1 = readBigwig(file = paste0(bw.path, "BIGWIG/D30_POS_I.bw"),
    chrom = "chr4", chromstart = 89000000, chromend = 91000000)

# mDAN D30 N2
bw.SNCA.mDAN.D30.2 = readBigwig(file = paste0(bw.path, "BIGWIG/D30_POS_II.bw"),
    chrom = "chr4", chromstart = 89000000, chromend = 91000000)

# mDAN D30 N3
bw.SNCA.mDAN.D30.3 = readBigwig(file = paste0(bw.path, "BIGWIG/D30_POS_III.bw"),
    chrom = "chr4", chromstart = 89000000, chromend = 91000000)

# mDAN D50 N1
bw.SNCA.mDAN.D50.1 = readBigwig(file = paste0(bw.path, "BIGWIG/HFFTHmCherry_D50_possort_S1.bw"),
    chrom = "chr4", chromstart = 89000000, chromend = 91000000)

# mDAN D50 N2
bw.SNCA.mDAN.D50.2 = readBigwig(file = paste0(bw.path, "BIGWIG/HFFTHmCherry_D50_possort_S3.bw"),
    chrom = "chr4", chromstart = 89000000, chromend = 91000000)

# mDAN D50 N3
bw.SNCA.mDAN.D50.3 = readBigwig(file = paste0(bw.path, "BIGWIG/HFFTHmCherry_D50_possort_S4.bw"),
    chrom = "chr4", chromstart = 89000000, chromend = 91000000)

# Add a scale next to the bigwig files - check the maximum to choose
scale.SNCA.max = max(c(bw.SNCA.smNPC.1$score,
                       bw.SNCA.smNPC.2$score,
                       bw.SNCA.smNPC.3$score,
                       bw.SNCA.mDAN.D15.1$score,
                       bw.SNCA.mDAN.D15.2$score,
                       bw.SNCA.mDAN.D15.3$score,
                       bw.SNCA.mDAN.D30.1$score,
                       bw.SNCA.mDAN.D30.2$score,
                       bw.SNCA.mDAN.D30.3$score,
                       bw.SNCA.mDAN.D50.1$score,
                       bw.SNCA.mDAN.D50.2$score,
                       bw.SNCA.mDAN.D50.3$score))

print(scale.SNCA.max)

# Define a small region of chr4
region.p.chr4.small = pgParams(chrom = "chr4",
                         chromstart = 89000000,
                         chromend = 91000000,
                         assembly = assembly(Genome = "hg38refGene",
                                               TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene",
                                               OrgDb = "org.Hs.eg.db"),
                         just = c("left", "top"),
                         width = 3.5,
                         fontcolor = "black",
                         fill = "black",
                         range = c(0, scale.SNCA.max))

# Plot Low-C data SNCA in mDAN D30 (10kb resolution)
chr4.SNCA.sq = plotHicTriangle(
    data = mDAN.D30.25kb,
    params = region.p.chr4.small,
    height = 1.75,
    resolution = 25000,
    x = 4.5,
    y = 5.5,
    zrange = c(0, 5),
    just = c("left", "top"), 
    default.units = "inches",
    palette = colorRampPalette(brewer.pal(n = 9, "YlGnBu")))

# ATACseq signal smNPC_I and scale
ATAC_smNPC_I = plotSignal(
  data = bw.SNCA.smNPC.1, 
  params = region.p.chr4.small,
  fill = "#313695", 
  alpha = 0.7, 
  linecolor = NA,
  x = 4.5, 
  y = 7.25, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

# ATACseq signal smNPC_II and scale
ATAC_smNPC_II = plotSignal(
  data = bw.SNCA.smNPC.2, 
  params = region.p.chr4.small,
  fill = "#313695", 
  alpha = 0.6, 
  linecolor = NA,
  x = 4.5, 
  y = 7.25, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

# ATACseq signal smNPC_III and scale
ATAC_smNPC_III = plotSignal(
  data = bw.SNCA.smNPC.3, 
  params = region.p.chr4.small,
  fill = "#313695", 
  alpha = 0.5, 
  linecolor = NA,
  x = 4.5, 
  y = 7.25, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_smNPC_III, 
          at = c(0, scale.SNCA.max),
          fontsize = 6)

plotText(label = "smNPC", 
         fontsize = 6, 
         fontcolor = "#313695",
         fontfamily = "Helvetica",
         x = 4.125, 
         y = 7.3125, 
         just = c("left", "top"),
         default.units = "inches",
         fontface = "bold")

# ATACseq signal mDAN D15 I and scale
ATAC_mDAN.D15_I = plotSignal(
  data = bw.SNCA.mDAN.D15.1, 
  params = region.p.chr4.small,
  fill = "#053061", 
  alpha = 0.7, 
  linecolor = NA,
  x = 4.5, 
  y = 7.625, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

# ATACseq signal mDAN D15 II and scale
ATAC_mDAN.D15_II = plotSignal(
  data = bw.SNCA.mDAN.D15.2, 
  params = region.p.chr4.small,
  fill = "#053061", 
  alpha = 0.6, 
  linecolor = NA,
  x = 4.5, 
  y = 7.625, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

# ATACseq signal mDAN D15 III and scale
ATAC_mDAN.D15_III = plotSignal(
  data = bw.SNCA.mDAN.D15.3, 
  params = region.p.chr4.small,
  fill = "#053061", 
  alpha = 0.5, 
  linecolor = NA,
  x = 4.5, 
  y = 7.625, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_mDAN.D15_III, 
          at = c(0, scale.SNCA.max),
          fontsize = 6)

plotText(label = "mDAN D15", 
         fontsize = 6, 
         fontcolor = "#053061",
         fontfamily = "Helvetica",
         x = 4.125, 
         y = 7.6875, 
         just = c("left", "top"),
         default.units = "inches",
         fontface = "bold")

# ATACseq signal mDAN D30 I and scale
ATAC_mDAN.D30_I = plotSignal(
  data = bw.SNCA.mDAN.D30.1, 
  params = region.p.chr4.small,
  fill = "#2D004B", 
  alpha = 0.7, 
  linecolor = NA,
  x = 4.5, 
  y = 8.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

# ATACseq signal mDAN D30 II and scale
ATAC_mDAN.D30_II = plotSignal(
  data = bw.SNCA.mDAN.D30.2, 
  params = region.p.chr4.small,
  fill = "#2D004B", 
  alpha = 0.6, 
  linecolor = NA,
  x = 4.5, 
  y = 8.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

# ATACseq signal mDAN D30 III and scale
ATAC_mDAN.D30_III = plotSignal(
  data = bw.SNCA.mDAN.D30.3, 
  params = region.p.chr4.small,
  fill = "#2D004B", 
  alpha = 0.5, 
  linecolor = NA,
  x = 4.5, 
  y = 8.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_mDAN.D30_III, 
          at = c(0, scale.SNCA.max),
          fontsize = 6)

plotText(label = "mDAN D30", 
         fontsize = 6, 
         fontcolor = "#2D004B",
         fontfamily = "Helvetica",
         x = 4.125, 
         y = 8.125, 
         just = c("left", "top"),
         default.units = "inches",
         fontface = "bold")

# ATACseq signal mDAN D50 I and scale
ATAC_mDAN.D50_I = plotSignal(
  data = bw.SNCA.mDAN.D50.1, 
  params = region.p.chr4.small,
  fill = "#003C30", 
  alpha = 0.7, 
  linecolor = NA,
  x = 4.5, 
  y =87.375, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

# ATACseq signal mDAN D50 II and scale
ATAC_mDAN.D50_II = plotSignal(
  data = bw.SNCA.mDAN.D50.2, 
  params = region.p.chr4.small,
  fill = "#003C30", 
  alpha = 0.6, 
  linecolor = NA,
  x = 4.5, 
  y = 8.375, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

# ATACseq signal mDAN D50 III and scale
ATAC_mDAN.D50_III = plotSignal(
  data = bw.SNCA.mDAN.D50.3, 
  params = region.p.chr4.small,
  fill = "#003C30", 
  alpha = 0.5, 
  linecolor = NA,
  x = 4.5, 
  y = 8.375, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_mDAN.D50_III, 
          at = c(0, scale.SNCA.max),
          fontsize = 6)

plotText(label = "mDAN D50", 
         fontsize = 6, 
         fontcolor = "#003C30",
         fontfamily = "Helvetica",
         x = 4.125, 
         y = 8.5, 
         just = c("left", "top"),
         default.units = "inches",
         fontface = "bold")

# Add gene name and genome labels for the chr4
# Add gene name
SNCA_g = plotGenes(params = region.p.chr4.small,
          x = 4.5,
          y = 8.8125, 
          height = 0.5,
          geneHighlights = data.frame(gene = c("SNCA"),
                        color = "red"),
          assembly = assembly(Genome = "hg38refGene", 
                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
                      OrgDb = "org.Hs.eg.db"),
          geneBackground = "black")

# Add genome label
annoGenomeLabel(plot = SNCA_g, 
                scale = "Mb", 
                axis = "x",
                x = 4.5, 
                y = 8.6875, 
                just = c("left", "top"))

pageGuideHide()
dev.off()
```

Process the results of the SNEEP pipeline
```{r, eval = FALSE, echo = TRUE}
## Take the smNPCs, TH+ neurons at day 15 - day 30 - day 50
## Load the data
# smNPC
SNEEP.smNPC = read_delim("/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/parkinsonDisease_project_Deborah_Lasse/sneep_witATAC_mergedlowC_2409/result_PD_smNPV_lowC_ATAC_merged_2409.txt",
                         delim = "\t",
                         col_names = TRUE)

# Add a column specifying the sample name
SNEEP.smNPC = SNEEP.smNPC %>% 
  mutate(Sample = "smNPC")

# Unique rSNPs 
SNEEP.smNPC %>% 
  distinct(SNP_position) %>% 
  write_delim("/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/uniq_rSNPs_smNPC.txt",
              delim = "\t",
              col_names = FALSE)

# How many unique target genes associated to those 91 PD-rSNPs found in smNPC
TG_smNPC = SNEEP.smNPC %>% 
  dplyr::select(SNP_position, geneNames) %>% 
  dplyr::filter(geneNames != ".") %>% 
  group_by(SNP_position, geneNames) %>% 
  distinct(SNP_position, .keep_all = TRUE) %>% 
  separate_rows(geneNames, sep = ",") %>% 
  ungroup() %>% 
  distinct(geneNames)

write_delim(TG_smNPC,
            "/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/enrichR/distinct_target_genes_smNPC.txt",
              delim = "\t",
              col_names = FALSE)

# 293 target genes are associated to 91 PD-rSNPs in smNPC

# TH+ neurons day 15
SNEEP.THposD15 = read_delim("/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/parkinsonDisease_project_Deborah_Lasse/sneep_witATAC_mergedlowC_2409/result_PD_mDAN_day15_lowC_ATAC_N1_2409.txt",
                         delim = "\t",
                         col_names = TRUE)

SNEEP.THposD15 = SNEEP.THposD15 %>% 
  mutate(Sample = "THpos_neurons_D15")

# Unique rSNPs 
SNEEP.THposD15 %>% 
  distinct(SNP_position) %>% 
  write_delim("/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/uniq_rSNPs_mDAND15.txt",
              delim = "\t",
              col_names = FALSE)

# How many unique target genes associated to those 180 PD-rSNPs found in mDAN D15
TG_mDAN.D15 = SNEEP.THposD15 %>% 
  dplyr::select(SNP_position, geneNames) %>% 
  dplyr::filter(geneNames != ".") %>% 
  group_by(SNP_position, geneNames) %>% 
  distinct(SNP_position, .keep_all = TRUE) %>% 
  separate_rows(geneNames, sep = ",") %>% 
  ungroup() %>% 
  distinct(geneNames)

write_delim(TG_mDAN.D15,
            "/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/enrichR/distinct_target_genes_mDAN_D15.txt",
              delim = "\t",
              col_names = FALSE)

# 308 target genes are associated to 180 PD-rSNPs in mDAN D15

# TH+ neurons day 30
SNEEP.THposD30 = read_delim("/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/parkinsonDisease_project_Deborah_Lasse/sneep_witATAC_mergedlowC_2409/result_PD_mDAN_day30_lowC_ATAC_N1_2409.txt",
                         delim = "\t",
                         col_names = TRUE)

SNEEP.THposD30 = SNEEP.THposD30 %>% 
  mutate(Sample = "THpos_neurons_D30")

# Unique rSNPs 
SNEEP.THposD30 %>% 
  distinct(SNP_position) %>% 
  write_delim("/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/uniq_rSNPs_mDAND30.txt",
              delim = "\t",
              col_names = FALSE)

# How many unique target genes associated to those 181 PD-rSNPs found in mDAN D30
TG_mDAN.D30 = SNEEP.THposD30 %>% 
  dplyr::select(SNP_position, geneNames) %>% 
  dplyr::filter(geneNames != ".") %>% 
  group_by(SNP_position, geneNames) %>% 
  distinct(SNP_position, .keep_all = TRUE) %>% 
  separate_rows(geneNames, sep = ",") %>% 
  ungroup() %>% 
  distinct(geneNames)

write_delim(TG_mDAN.D30,
            "/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/enrichR/distinct_target_genes_mDAN_D30.txt",
              delim = "\t",
              col_names = FALSE)

# 301 target genes are associated to 181 PD-rSNPs in mDAN D30

# TH+ neurons day 50
SNEEP.THposD50 = read_delim("/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/parkinsonDisease_project_Deborah_Lasse/sneep_witATAC_mergedlowC_2409/result_PD_mDAN_day50_lowC_ATAC_N1_2409.txt",
                         delim = "\t",
                         col_names = TRUE)

SNEEP.THposD50 = SNEEP.THposD50 %>% 
  mutate(Sample = "THpos_neurons_D50")
